---
title: "GroupProject_MeasuringReefs_Yan"
author: "Yan"
date: "`r format(Sys.Date())`" 
output: 
  github_document
---

## Introduction



## Method

As the reference shown below: 

<em>https://github.com/MBIO630-Remote-Sensing-2022/MBIO630_GroupProject_MeasuringReefs/blob/main/MBIO630_GroupProject_MeasuringReefs.md</em> 

## Result

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sciplot)
library(vegan)
library(plotrix)
library(plyr)
library(cowplot)
library(ggplot2)
library(fishualize)
```


```{r data import, echo=TRUE, results='hold', include=FALSE}
################################################
# import data, observe structure
################################################

data<-read.csv("data/MeasuringReefs_Master.csv", header = TRUE)

names(data)
data$year<-substr(data$date,0,4) # add a column for year only
head(data)

plot_data_20 <- 
  data %>%
  filter(reef_no == 20) 
plot_data_22 <- 
  data %>%
  filter(reef_no == 22) #separate data from two reefs

```

Effect of method. Two patch reefs show similar pattern of their method differences.

```{r data explore-1, echo=FALSE, results='hide', fig.height=5, fig.width=5, fig.align='center', warning=FALSE}

################################################
# explore patterns
################################################

# Effect of method

p1_1 <- ggplot(data = plot_data_20, aes(x = method, y = area_m2, fill = method, na.rm = TRUE)) +
    geom_boxplot()+
    ylab("Patch reef area (m^2)")+ 
  xlab(element_blank())+
  ggtitle("Area versus method #20")+
  theme_light()+
  scale_fill_grey()+
  theme(legend.position = "none")
dev.copy(png,"output/method_area_effect_20.png")    # can change to .png, etc.; can change size to incr resolution
dev.off()

p1_2 <- ggplot(data = plot_data_22, aes(x = method, y = area_m2, fill = method, na.rm = TRUE)) +
    geom_boxplot()+
    xlab("Method")+
    ylab("Patch reef area (m^2)")+ 
  ggtitle("Area versus method #22")+
  theme_light()+
  scale_fill_grey()+
  theme(legend.position = "none")
dev.copy(png,"output/method_area_effect_22.png")    # can change to .png, etc.; can change size to incr resolution
dev.off()

p1 <- plot_grid(p1_1,p1_2, nrow = 2,align="h",labels=c())
p1
                
aggregate(plot_data_20$area_m2, by=list(type=plot_data_20$method), mean, na.rm = TRUE)
aggregate(plot_data_20$area_m2, by=list(type=plot_data_20$method), sd, na.rm = TRUE)

aggregate(plot_data_22$area_m2, by=list(type=plot_data_22$method), mean, na.rm = TRUE)
aggregate(plot_data_22$area_m2, by=list(type=plot_data_22$method), sd, na.rm = TRUE)
```

Effect of imagery resolution on area and perimeter

```{r data explore-2, echo=FALSE, results='hide', fig.height=5, fig.width=5, fig.align='center', warning=FALSE, message=FALSE}
# Effect of imagery resolution

## on area

p2_1 <- ggplot(data = plot_data_20, aes(x = imagery_resolution_m, y = area_m2, na.rm = TRUE)) +
    geom_point(shape=21)+
    xlab("Imagery spatial resolution (m)")+
    ylab("Patch reef area (m^2)")+ 
  ggtitle("Area vs resolution \n #20")+
  geom_smooth(method="lm", colour="black", size=0.5)+
  theme_light()+
  theme(legend.position = "none")

p2_2 <- ggplot(data = plot_data_22, aes(x = imagery_resolution_m, y = area_m2, na.rm = TRUE)) +
    geom_point(shape=21)+
    xlab("Imagery spatial resolution (m)")+
    ylab("Patch reef area (m^2)")+ 
  ggtitle("Area vs resolution \n #22")+
  geom_smooth(method="lm", colour="black", size=0.5)+
  theme_light()+
  theme(legend.position = "none")

## on perimeter

p2_3 <- ggplot(data = plot_data_20, aes(x = imagery_resolution_m, y = perimeter_m, na.rm = TRUE)) +
    geom_point(shape=21)+
    xlab("Imagery spatial resolution (m)")+
    ylab("Patch reef perimeter (m)")+ 
  ggtitle("Perimeter vs resolution \n #20")+
  geom_smooth(method="lm", colour="black", size=0.5)+
  theme_light()+
  theme(legend.position = "none")

p2_4 <- ggplot(data = plot_data_22, aes(x = imagery_resolution_m, y = perimeter_m, na.rm = TRUE)) +
    geom_point(shape=21)+
    xlab("Imagery spatial resolution (m)")+
    ylab("Patch reef perimeter (m)")+ 
  ggtitle("Perimeter vs resolution \n #22")+
  geom_smooth(method="lm", colour="black", size=0.5)+
  theme_light()+
  theme(legend.position = "none")

p2 <- plot_grid(p2_1,p2_2,p2_3,p2_4, nrow = 2,align="h",labels=c())
p2

```

\n Effect of date (i.e., do patch reefs measurably grow or shrink over time?)

**We can not measure the growth of patch reefs in this data set** due to low resolution and its overestimation in the recent years. If the data is usable, these two patch reefs should show similar growth rate (slope in the fig) because they grew in adjacent area. 

```{r data explore-3, echo=FALSE, results='hide', fig.height=5, fig.width=5, fig.align='center', warning=FALSE, message=FALSE}

p3_1 <- ggplot(data = plot_data_20, aes(x = as.numeric(year), y = area_m2, na.rm = TRUE)) +
    geom_point(shape=21)+
    xlab("Year")+
    ylab("Patch reef area (m^2)")+ 
  ggtitle("Area versus year #20")+
  geom_smooth(method="lm", colour="black", size=0.5)+
  theme_light()+
  theme(legend.position = "none")

p3_2 <- ggplot(data = plot_data_22, aes(x = as.numeric(year), y = area_m2, na.rm = TRUE)) +
    geom_point(shape=21)+
    xlab("Year")+
    ylab("Patch reef area (m^2)")+ 
  ggtitle("Area versus year #22")+
  geom_smooth(method="lm", colour="black", size=0.5)+
  theme_light()+
  theme(legend.position = "none")

p3 <- plot_grid(p3_1,p3_2, nrow = 2,align="h",labels=c())
p3

#看不出成長 因為不同年份解析度不同，而且越近的年份解析度越差

```

\n Now, let's see if there's anything going on with time when imagery resolution is considered:

The result shows that **"Resolution" have more influence** in linear regression model. Drop "year" can decrease AIC and have better model. In addition, the **y ~ x1+x2** model is better than y ~ x1*x2 model. 

```{r data analysis-1, echo=FALSE, results='hold'}

################################################
# analyze data
################################################

# Effects of imagery resolution + year

## Note: interpretation below is for my test data; your data's results may be different
data$year <- as.numeric(data$year) 
#res.year.lm=lm(area_m2 ~ imagery_resolution_m * year, data=data) # run interaction model
#summary(res.year.lm)      # overall model is significant, but not indiv parameters (ie, predictor variables)
#anova(res.year.lm)        # run ANOVA to look at predictor variables in isolation
#drop1(res.year.lm, test="F")  # use drop1 function to see which parameter can be dropped (test="F" adds type 
                          # II ANOVA)
res.year.lm2 <- lm(area_m2 ~ imagery_resolution_m + year, data=data)
                          # re-run model w/o interaction term that drop1 said to drop
summary(res.year.lm2)     # model now says both predictor variables are significant
drop1(res.year.lm2, test="F") # drop1 says neither remaining variable can be dropped

```


Or reef identity (reef number):

The result shows that **both "reef ID" and "resolution" should not be dropped**.

```{r data analysis-2, echo=FALSE, results= 'hold'}

################################################
# analyze data
################################################

# Effects of imagery resolution + reef ID
#res.reefID.lm=lm(area_m2 ~ imagery_resolution_m * reef_no, data=data)
#summary(res.reefID.lm)
#drop1(res.reefID.lm, test="F")

res.reefID.lm=lm(area_m2 ~ imagery_resolution_m + reef_no, data=data)
summary(res.reefID.lm)
drop1(res.reefID.lm, test="F")
```

Analyze the trade-offs between the different imagery

```{r data analysis-3, echo=FALSE, results='hide', fig.height=5, fig.width=5, fig.align='center', warning=FALSE}

################################################
# analyze the trade-offs between the different imagery
################################################

boxplot(imagery_resolution_m~platform, data=data, na.ignore=TRUE, col="lightgrey",
     ylab="Resolution (m/pix)", 
     xlab="Platform", 
     main="Resolution versus Platform")
```

Analyze the difference between observers. We can find that there are **three outliers** in patch reef #20. Apart from that, the **measurement between different observers is consistent**. 

```{r data analysis-4, echo=FALSE, results='hide', fig.height=5, fig.width=5, fig.align='center', warning=FALSE}

################################################
# analyze the difference between observers
################################################

p4_1 <- ggplot(data = plot_data_20, aes(x = observer, y = area_m2, fill = observer, na.rm = TRUE)) +
    geom_boxplot()+
    xlab("observer")+
    ylab("Patch reef area (m^2)")+ 
  ggtitle("Area versus method #20")+
  theme_light()+
  scale_fill_grey()+
  theme(legend.position = "none")

p4_2 <- ggplot(data = plot_data_22, aes(x = observer, y = area_m2, fill = observer, na.rm = TRUE)) +
    geom_boxplot()+
    xlab("observer")+
    ylab("Patch reef area (m^2)")+ 
  ggtitle("Area versus method #22")+
  theme_light()+
  scale_fill_grey()+
  theme(legend.position = "none")

p4 <- plot_grid(p4_1,p4_2, nrow = 2,align="h",labels=c())
p4
```

## Discussion 

#### 1.Which method did you find to be more variable among groups/individuals - field or imagery?

* Imagery is more variable than field among groups.
* The reason might be due to the multiple data sources of imagery, such as aerial and satellites. The resolution of images, filming angle (nadir or tilted) and quality of images (weather, sunshine intensity or quality of optical sensors) among multiple data sources might cause uncertainty of measurement and increase its variability. 


#### 2.How did imagery resolution affect your measurements?

Lower imagery resolution tend to overestimate patch reef area. Moreover, larger patch reef (#20) tend to be overestimated more obviously. Surface area would have more overestimation than perimeter. Or these might be just due to the outliers in #20. 
We need more data across different size of reefs to make sure whether larger size would have more overestimation.

#### 3.What are the trade-offs between field vs imagery measurements?

|Measurements            | pros       | cons    | 
|:---                 | :---          | :---      |
|Field              | lower variability, can be more precise and accurate, can get the data whenever we want | time-consumed, investment of our own measuring equipment (such as handheld GPS and boat) is needed   |
|Imagery            | free data resources are available, measurement can be verified by different people and multiple times,  can be measured rapidly | higher variability, need extra cost to get higher quality data, desired data at certain time might be limited|

#### 4.What are the trade-offs between the different imagery a) platforms and b) resolutions?

|a) Platforms            | pros       | cons    | 
|:---                 | :---          | :---      |
|Google Earth              | free, have higher resolution, can save the measurement results and study sites,  | database of images is smaller, no filter for searching images,  Graphical User Interface is out-of-date  |
|Planet Exlorer            | database of images is larger, have filter for searching images, Graphical User Interface is fancy | registration is needed to access data and might be rejected, the measurement tools is inconvenient, many images have low resolution |

|b) Resolution            | pros       | cons    | 
|:---                 | :---          | :---      |
|High | measurement can be more precise and accurate, can measure smaller research targets | data might be  expensive or limited, larger storage space is needed |
|Low | data is easy to access, can be shown smoothly in computer | measurement might have high variability, cannot measure smaller research targets |


#### 5.How should we measure the growth rate of reefs in imagery?
The resolution of data should keep consistent. Or the variation that is caused by resolution should be smaller than growth rate.  

